---
title: "git-posit-test"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro paragraph

Example of document that will be automatically published to Connect as new commits
are being pushed to the Github repo

```{r cars}
summary(cars)
```

## New content
This content should appear automatically on the Connect published after this change 
is pushed to Github. This new content appeared at `r Sys.time()`

## Another paragraph
Adding another paragraph as my previous change was not picked-up.

## Testing automatic updates
updates are driven by the `manifest.json` file, so `rsconnect::WriteManifest` has
to be run before pushing any commit to the Github repo.

## Yet another section because changes are not being picked up...
I update the config file to check for changes every 5 minutes. Let's see if it works.
additional minor change. My understanding of what is happening is the following:
- Some kind of automatic check update is happening
- But it is not working...
- Now, if I try to refresh, no changes are being detecting (even though the Github 
version is different)
- If I push a change now before the next automatic check runs, the report will successfully refresh
Testing...
